---
title: "McDonald's, Restaurants, and Income"
author: "Leon Luc, lluc507@ucla.edu"
output:
  html_document:
    fig_caption: yes
    force_captions: yes
    highlight: pygments
    number_sections: yes
    theme: cerulean
csl: mee.csl
---
```{r, echo = FALSE, results = 'hide', message = FALSE, warning = FALSE}
1.
GroupEast <- read.csv("GroupEast.csv", stringsAsFactors = FALSE)
dim(GroupEast)

irsCAzip2013 <- read.csv("irsCAzip2013.csv", stringsAsFactors = FALSE)
dim(irsCAzip2013)

2.
#A.
names(GroupEast)
GroupEast <- GroupEast[-c(3,7:9,16,30,33:34,36:39)]
#B.
GroupEast <- GroupEast[-which(is.na(GroupEast$Latitude)),]

GroupEast <- GroupEast[order(GroupEast$Latitude),]
rownames(GroupEast) <- 1:nrow(GroupEast)
which(GroupEast$Latitude == 0)

addresses <- paste(GroupEast$Street.Address[1:254], GroupEast$City[1:254], GroupEast$State[1:254], sep = ", ")
head(addresses)

library(ggmap)
#locg <- geocode(addresses, output="latlona", messaging=FALSE, source="google")
#save(locg, file="locg.Rda")
load("locg.Rda")
GroupEast$Longitude[1:254] <- locg$lon
GroupEast$Latitude[1:254] <- locg$lat
which(is.na(GroupEast$Latitude)) # Only "Pasta Bravo" didn't get geocoded
#C.
GroupEast[,c(9,12,13,15:27)][GroupEast[,c(9,12,13,15:27)] == " "] <- NA
#D.
GroupEast$NumRating <- gsub("/ 5", "", GroupEast$Ratings)
GroupEast$NumRating <- as.numeric(GroupEast$NumRating)
#E.
names(GroupEast)[5] <- c("Zip")
GroupEast <- GroupEast[,c(1:5,28:29,6:9,30,10:27)]

3.
#A.
sort(table(GroupEast$Ratings))
sort(table(GroupEast$NumRating, useNA = "always"))

library(knitr)
score <- data.frame(table(GroupEast$NumRating))
names(score) <- c("Rating", "Frequency")
#B.
sort(table(GroupEast$Alcohol))
table(GroupEast$Credit.Cards)
table(GroupEast$Good.for.Kids)
#C.
apply(irsCAzip2013[,c("N1", "MARS1", "MARS2", "MARS4", "NUMDEP", "A00100")], 2, summary)
IRS <- data.frame(apply(irsCAzip2013[,c("N1", "MARS1", "MARS2", "MARS4", "NUMDEP", "A00100")], 2, summary))

4.
#A.
names(irsCAzip2013)[1] <- "Zip"
#B.
irsCAzip2013 <- irsCAzip2013[,c(1:5,8:9)]
head(irsCAzip2013)
#C.
YelpIRS <- merge(GroupEast, irsCAzip2013, by = "Zip")
dim(YelpIRS)
head(YelpIRS)

5.
#A.
library(XML)
#McDonalds <- readHTMLTable("http://www.stat.ucla.edu/~vlew/datasets/mcdonaldsG.html", stringsAsFactors = FALSE)
#McDonalds <- data.frame(McDonalds)
#save(McDonalds, file = "McDonalds.Rda")
load("McDonalds.Rda")
class(McDonalds)
dim(McDonalds)
names(McDonalds) <- c("Store", "Address", "City", "State", "Zip", "Phone", "Longitude", "Latitude", "InWalmart", "Playplace")
#B.
CA_McD <- McDonalds[McDonalds$State == "CA",]
CA_McD <- CA_McD[order(CA_McD$Zip),]

count <- data.frame(tapply(CA_McD$Latitude, CA_McD$Zip,length)) # dplyr CA_McD %>% group_by(Zip) %>% count()
count$Zip <- row.names(count)
count <- count[-1,]
names(count)[1] <- "NumOfMcDonalds"
count[,1] <- as.character(count[,1])
final <- merge(YelpIRS, count, by = "Zip")
dim(final)

6.
library(ggplot2)
g1 <- ggplot(final, aes(x=A00100, y= NumOfMcDonalds))
g1 + geom_point(aes(color=NumOfMcDonalds)) + labs(title = "# of McDonald's in Zip Code vs. AGI", x = "Zip Code", y = "Adjusted Gross Income") + geom_smooth(method = "lm", color = "black", formula = y~x)

#basic
boxplot(final$A00100 ~ final$Credit.Cards, main = "Boxplot of Adjusted Gross Income over Credit Cards at Restaurants", col = "turquoise1", xlab = "Accepts Credit Cards", ylab = "A00100")

7.
final$propAGI <- round(final$A00100/max(final$A00100), 3)

8.
mod <- lm(final$A00100 ~ final$NUMDEP)
cor(x = final$NUMDEP, y = final$A00100)
mod$coefficients
mean(mod$fitted.values)

9.
round(tapply(final$NumRating, final$Zip, mean, na.rm=TRUE), 2)

rating <- data.frame(round(tapply(final$NumRating, final$Zip, mean, na.rm=TRUE), 2))
set.seed(318)
rating <- data.frame(rating[sample(nrow(rating),10),])
names(rating) <- "Mean Rating"
```


# Results
## Tables
This first table comes from task 3A and it surprised me that the restaurants are mostly rated 5 stars. I always felt that people who submitted ratings on Yelp were very unsatisfied and more likely to take the time to give low ratings than those who were satisfied.
```{r, echo = FALSE}
kable(score)
```
     
The next table below comes from task 3C and I chose to output this because I feel that it gives a sense of what the IRS data is. Not many people understand what the variables mean and so providing an overall summary of the data provides a basic understanding of the numbers.
```{r, echo = FALSE}
kable(IRS, align = "l", caption = "Table: A summary table of the IRS data.")
```
     
This last table comes from task 9 and it shows the average ratings for the restaurants in each zip code. Only a sample of all of the zip codes are shown, but it is interesting to see the different scores across zip codes of California.
```{r, echo = FALSE}
kable(rating, align = "l", caption = "Table: This is a sample of the mean rating of restaurants per zip code.")
```

## Graphics
The first graphic below is a ggplot and I wanted to see if there was a relationship between the amount of McDonald's in a zip code and the adjusted gross income of individuals from the area code. It turned out that there was not really a clear relationship.
```{r irisDataPlot, echo = FALSE, fig.cap="Figure 1: Relationship between Number of McDonald's in a zip code and adjusted gross income of individuals in the zip code. The line represents the conditional mean."}
 #ggplot
library("ggplot2", lib.loc="~/R/win-library/3.2")
g1 <- ggplot(final, aes(x=Zip, y= A00100))
g1 + geom_point(aes(color=NumOfMcDonalds)) + labs(title = "# of McDonald's in Zip Code vs. AGI", x = "Zip Code", y = "Adjusted Gross Income") + geom_smooth(method = "lm", color = "black", formula = y~x)
```

The second graphic below is a box plot made using base R. This visual is something that I would expect since a person who uses a credit card typically has more money and so would likely use it at restaurants.
```{r, echo = FALSE}
#basic
boxplot(final$A00100 ~ final$Credit.Cards, main = "Boxplot of Adjusted Gross Income over Credit Cards at Restaurants", col = "turquoise1", xlab = "Accepts Credit Cards", ylab = "A00100")
```

# Extras
## Conclusion/Discussion/Application
  Coming into this class, I was a little nervous because I thought that I was at a disadvantage by being a sophomore who had no prior exposure to R or upper-divison classes that may have used R. I became pleasantly surprised that I was able to keep up and stay on top of my work for the duration of the quarter. As a second year Statistics major, I foresee that I will be using R much more in the future as I tackle on the upper-division courses. I think Stats 20 has provided me the foundation to do well with R and hopefully I will not have any troubles when I do eventually take those classes. Going further ahead into the future, I may perhaps use R in my job and if I do, I will be glad that I learned what it was.
